---
title: "FML_Assignment 4"
author: "Manaswini"
date: '2022-03-17'
output:
  word_document: default
  pdf_document: default
---
```{r}
setwd("C:/Users/mpuru/OneDrive/Documents/R/Assignment4_fml")
Pharmaceuticals <- read.csv("~/R/Assignment4_fml/Pharmaceuticals.csv")
View(Pharmaceuticals)
head(Pharmaceuticals)


```

```{r}

dim(Pharmaceuticals) #Dataframe has 14 variables and 21 records
str(Pharmaceuticals) #Shows the No. of variable and their datatypes
U<-unique(Pharmaceuticals) # This shows there are no duplicate rows
dim(U) 



```
```{r}
pairs(Pharmaceuticals[3:11]) #All possible combinations of Discrete variables plotted
library(DataExplorer)
introduce(Pharmaceuticals) #Shows the number of Discrete/continuous variables and missing value, if any.
#There are 5 discrete Variables, 9 Continuous variables and no missing variables.

```
```{r}
set.seed(64060)
plot(Market_Cap~Rev_Growth, Pharmaceuticals)
with(Pharmaceuticals, text(Market_Cap~Rev_Growth, labels=Symbol, pos=4, cex=0.4)) #A rough estimate of how the distribution is for Market cap vs revenue growth
plot(Market_Cap~Net_Profit_Margin, Pharmaceuticals)
with(Pharmaceuticals, text(Market_Cap~Net_Profit_Margin, labels=Symbol, pos=4, cex=0.4))

```
```{r}
#K-means clustering model
library(tidyverse)
library(factoextra)
library(ISLR)
Pharmaceuticals1 <- scale(Pharmaceuticals[, c(3:11)], center = TRUE, scale = TRUE)
dist_pharmaceuticals <- get_dist(Pharmaceuticals1)
print(dist_pharmaceuticals, digits = 3)
heatmap(Pharmaceuticals1, scale = "column")



```


```{r}
#Company 8 and 17 are the furthest from each other as the distance between them is the largest i.e 7.18. 
Pharmaceuticals[c(8,17),] #From this we can see that there is a huge difference in terms of Market capital, Rev_Growth and Net Profit margin of both these companies
boxplot(Pharmaceuticals1, col=c("deepskyblue","deepskyblue4","cadetblue","cadetblue1","cadetblue2","cadetblue3","cadetblue4","dodgerblue", "dodgerblue4"), las = 2) #visualization of the outliers

```
Finding optimal number for K as per Elbow method

```{r}
fviz_nbclust(Pharmaceuticals1, kmeans, method = "wss") +
 geom_vline(xintercept = 2, linetype = 5)       #Elbow method

fviz_nbclust(Pharmaceuticals1, kmeans, method = "silhouette") #Silhouette Method

```
Silhouette method of finding optimal number of K is highly influenced by outliers. Since our data has quite a few number of outliers. 

On removing the outliers, the optimal value of K using the silhouette method also came out to be 2.

Hence, We can consider the optimal number of K using the Elbow method.
```{r}
#k=2

k_mean_model2 <- kmeans(Pharmaceuticals1, centers = 2, nstart = 25) 
fviz_cluster(k_mean_model2, data = Pharmaceuticals1)+ labs(subtitle = "k=2")
k_mean_model2 


```
# b. Interpret the clusters with respect to the numerical variables used in forming the clusters.

Companies in cluster 2 have a higher Return on Equity than companies in cluster 1 for the identical Return on Equity values.

# c. Is there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in forming the clusters) 
 
Cluster 1 has highest rev_growth, highest net_profit_margin and has hold median recommendation.

Cluster 2 has low rev_growth, high net_profit_margin and has moderate buy recommendation.
 
# d. Provide an appropriate name for each cluster using any or all of the variables in the dataset.

High market cap companies : cluster 1

Low market cap companies : cluster 2



















