---
output:
  pdf_document: default
  html_document: default
---
#title: "Assinment2FML"
#author: "Mpurumandla"
#date: "20/02/2022"
#output: pdf_document

#Importing data and setting data as working directory
```{r}
UniversalBank <- read.csv("universalbank.csv")

colnames<-c('ID','Age','Experience','Income','zIP.Code','Family','CCAvg','Education','Mortgage','Personal.Loan','Securities.Account','CD.Account','Online','Creditcard')

summary(UniversalBank)
```


#Removing some of attributes we do not use in our model and set them to NULL
```{r}
UniversalBank$ID <- NULL 
UniversalBank$ZIP.Code <- NULL

summary(UniversalBank)

```

# Calling Libraries
```{r}
library(class)
library(dplyr)
library(caret)
library(ggplot2)

summary(UniversalBank)


```

# converting categorical variables("Education","Personal.Loan") to factors
```{r}
UniversalBank$Personal.Loan=as.factor(UniversalBank$Personal.Loan)
UniversalBank$Income=as.factor(UniversalBank$Income)
Bank_norm<-UniversalBank

```

# Normalize the data,removing target attribute before normalization
```{r}
Norm_model<-preProcess(UniversalBank[,-8],method = c("center", "scale"))
Bank_norm[, -8]=predict(Norm_model,UniversalBank[,-8])
summary(Bank_norm)
Bank_norm$personal.Loan=UniversalBank$Personal.Loan

```

#Dividing the data into train and validation. 
```{r}
Train_Index = createDataPartition(UniversalBank$Personal.Loan,p=0.6, list=FALSE) # 60% reserved for Train
Train.df=Bank_norm[Train_Index,]
Validation.df=Bank_norm[-Train_Index,]

```

#1 -> Modelling k-NN with K=1 and sample data

```{r}
To_Predict=data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, 
                            Mortgage = 0, Securities.Account = 0, CD.Account =0, Online = 1, CreditCard = 1,Education = 1)

print(To_Predict)
To_Predict_norm=predict(Norm_model,To_Predict)
print(To_Predict_norm)
Prediction <-knn(train=Train.df[,1:7], 
                 test=To_Predict_norm[,1:7],
                 cl=Train.df$Personal.Loan,
                 k=1)
print(Prediction)

```

#2- Finding the best value of K to avoid over fitting
```{r}
fitControl <- trainControl(method = "repeatedcv",
                           number = 3,
                           repeats = 2)
searchGrid=expand.grid(k = 1:10)
Knn.model=train(personal.Loan~., 
                data=Train.df,
                method='knn',
                tuneGrid=searchGrid,
                trControl = fitControl,)
Knn.model

```

#3 - Show the confusion matrix for the validation data that results from using the best k.
```{r}
predictions<-predict(Knn.model,Validation.df)

confusionMatrix(predictions,Validation.df$Personal.Loan)


```

#4

```{r}
To_Predict=data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, 
Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1, CreditCard = 1,Education = 1)


print(To_Predict)
To_Predict_norm=predict(Norm_model,To_Predict)
print(To_Predict_norm)
Prediction <-knn(train=Train.df[,1:7], 
                 test=To_Predict_norm[,1:7],
                 cl=Train.df$Personal.Loan,
                 k=1)
Prediction
 

```

#5

```{r}
splitSample <- sample(1:3, size=nrow(Bank_norm), prob=c(0.5,0.3,0.2), replace = TRUE)
train_Data <- Bank_norm[splitSample==1,]
valid_Data <- Bank_norm[splitSample==2,]
test_Data <- Bank_norm[splitSample==3,]

Predict=data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education= 1,Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1,CreditCard = 1)

print(Predict)

Predict_norm<-predict(Norm_model,Predict)

print(Predict_norm)

Prediction_newsplit <-knn(train=Train.df[,1:7,9:12], 
                          test=To_Predict_norm[,1:7,9:12],
                          cl=Train.df$Personal.Loan,
                          k=1)

print(Prediction_newsplit)

fitControl2 <- trainControl(method = "repeatedcv",
                            number = 3,
                            repeats = 2)
searchGrid=expand.grid(k = 1:10)

Knn.model2 =train(Personal.Loan~., 
                  data=Train.df,
                  method='knn',
                  tuneGrid=searchGrid,
                  trControl = fitControl2,)
Knn.model2

predictions2<-predict(Knn.model2,Validation.df)
confusionMatrix(predictions2,Validation.df$Personal.Loan)


```




